---
title: "Stops"
author: "Ayush Chandra"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)

x <- stops |>
  filter(race %in% c("black", "white")) |>
  mutate(race = str_to_title(race), 
         sex = str_to_title(sex))

```



$$
P(Y = 1) = \frac{1}{1 + e^{-(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n)}}
$$

with \( Y \sim \text{Bernoulli}(\rho) \) where \( \rho = \frac{1}{1 + e^{-(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n)}} \)


$$
\widehat{\text{arrested}} = 0.177 
+ 0.0614 \cdot \text{sex}_{\text{Male}} 
- 0.0445 \cdot \text{race}_{\text{White}} 
+ 0.0146 \cdot \text{zone}_{\text{B}} 
+ 0.00610 \cdot \text{zone}_{\text{C}} 
+ 0.0781 \cdot \text{zone}_{\text{D}} 
+ 0.00190 \cdot \text{zone}_{\text{E}} 
- 0.00271 \cdot \text{zone}_{\text{F}} 
+ 0.0309 \cdot \text{zone}_{\text{G}} 
+ 0.0757 \cdot \text{zone}_{\text{H}} 
+ \text{(interaction terms for race and zone)}
$$

```{r}
#| cache: true
fit_stops <- linear_reg() |>
    set_engine("lm") |>
    fit(arrested ~ sex + race*zone, data = x)
```


Racial arguments in policing outcomes remain an important issue, particularly when examining how factors like race and location influence the likelihood of an arrest during traffic stops. Using data from a study of New Orleans drivers, we wish to understand how driver race can have an impact on the probability of getting arrested during a traffic stop. One weakness is that the study is taken from a small place in New Orleans, therefore it doesn't fully represent the entire US population.
