---
title: "Stops"
author: "Ayush Chandra"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(marginaleffects)

x <- stops |>
  filter(race %in% c("black", "white")) |>
  mutate(race = str_to_title(race), 
         sex = str_to_title(sex))

```


```{r}
#| cache: true
fit_stops <- linear_reg() |>
    set_engine("lm") |>
    fit(arrested ~ sex + race*zone, data = x)

#| label: augment-model
#| message: false
#| warning: false

preds <- augment(fit_stops, new_data = x)

```

```{r}
#| label: tidy-table
#| echo: false
#| message: false
#| warning: false

library(gt)

tidy(fit_stops) |>
  mutate(term = str_replace_all(term, "sex", "Sex: "),
         term = str_replace_all(term, "race", "Race: "),
         term = str_replace_all(term, "zone", "Zone: "),
         estimate = round(estimate, 3),
         std.error = round(std.error, 3),
         statistic = round(statistic, 2),
         p.value = signif(p.value, 3)) |>
  gt() |>
  tab_header(
    title = "Linear Regression Results",
    subtitle = "Effect of Race, Sex, and Zone on Arrest Probability"
  ) |>
  cols_label(
    term = "Predictor",
    estimate = "Estimate",
    std.error = "Std. Error",
    statistic = "t value",
    p.value = "p value"
  ) |>
  fmt_number(columns = c(estimate, std.error, statistic, p.value), decimals = 3) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) |>
  opt_table_outline() |>
  opt_row_striping()

```

```{r}
#| label: beautiful-plot
#| fig-cap: "Predicted Arrest Rate by Race, Zone, and Sex"
#| fig-width: 10
#| fig-height: 6
#| warning: false

preds |>
  ggplot(aes(x = zone, y = .pred, color = race, linetype = sex, group = interaction(race, sex))) +
  stat_summary(fun = mean, geom = "line", size = 1.2) +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 21, fill = "white") +
  scale_color_manual(values = c("Black" = "#1f77b4", "White" = "#ff7f0e")) +
  scale_linetype_manual(values = c("Male" = "solid", "Female" = "dashed")) +
  labs(
    title = "Predicted Arrest Rate by Race, Zone, and Sex",
    subtitle = "Model-based averages from linear regression",
    x = "Zone",
    y = "Predicted Arrest Rate",
    color = "Race",
    linetype = "Sex"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 18),
    legend.position = "right",
    panel.grid.minor = element_blank()
  )

```

Racial arguments in policing outcomes remain an important issue, particularly when examining how factors like race and location influence the likelihood of an arrest during traffic stops. Using data from a study of New Orleans drivers, we wish to understand how driver race can have an impact on the probability of getting arrested during a traffic stop. One weakness is that the study is taken from a small place in New Orleans, therefore it doesn't fully represent the entire US population. We model our outcome variable, arrested, as a linear function of sex, race, and zone. From this, we examined that Males are less likely of getting arrested than Females. We estimate that the probability of a Black driver in New Orleans getting arrested during a traffic stop is roughly 5% more than the probability for White drivers.
